\section{PROJECTS}

% ------- DEFINE PROJECT LAYOUT
\newcommand*{\project}[4][.25em]{
  % \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {#3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
	\par\addvspace{#1}}

{\project{Information Retrieval and Web Search Engine}{Oct 2017 - Nov 2017}
	{\begin{itemize}
		\item Developed a web search engine to retrieve and search CNN news using Crawler4j and Apache Solr.
		\item Applied Page Rank for search, supported auto completion and spell correction features.
		\item Utilized jQuery and Materialize for front-end, PHP for back-end.
  	\end{itemize}
  }
}

{\project{Collaborative Online Code Playground}{Aug 2017 - Oct 2017}
	{\begin{itemize}
		\item Designed and developed a single-page web application deployed on AWS for users to register, login, edit questions and code online using Auth0, Angular 4, Node.js and MongoDB.
		\item Created a code editor for multiple users to edit simultaneously by implementing Socket.io, Redis and ACE source.
		\item Built a code executor service with Flask to compile and execute Java, C++, Python codes inside Docker Unix image.
		\item Decoupled services using RESTful API and implemented load balance using Nginx to improve system throughput.
  	\end{itemize}
  }
}

{\project{Kernel Development for Weenix OS}{May 2017 - Jun 2017}
	{\begin{itemize}
		\item Implemented threads, processes, scheduling and synchronization primitives on Unix-like Weenix OS.
		\item Developed virtual file system and virtual memory in C, managed address spaces and run user-level code.
		\item Tested, debugged kernel in GDB, and use Git for version control.
  	\end{itemize}
  }
}

{\project{Facebook Search, Web and Android Application}{Jan 2017 - Mar 2017}
	{\begin{itemize}
		\item Designed responsive websites for information retrieval of Facebook entities using Facebook SDK and Graph API.
		\item Enhanced user experience at front-end using AngularJS and Bootstrap and constructed backend server logic for data processing and JSON response with PHP on AWS.
		\item Developed an Android app as mobile version for the web application using Android SDK in Java.
  	\end{itemize}
  }
}

{\project{Socket Programming for Distributed Computing}{Oct 2016 - Nov 2016}
	{\begin{itemize}
		\item Constructed a computational offloading model where a single client offloads computation to and collected results from a web server which in turn distributed the load over another three backend servers.
		\item Established communications among a client, a web server and several backend servers over TCP and UDP connections by programming sockets with C++ in Linux after preprocessing.
  	\end{itemize}
  }
}
